Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-08 papers/ms.tex
ms: add words about Hα

@@

Gaia source lists and abbreviated info.  Include rotation periods.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Key spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown as in the observed frame, and
    the stars are sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
			\includegraphics[width=0.49\textwidth]{f6b.pdf}
		}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Lithium 6708\AA\ equivalent widths for Kepler-1643, KOI-7368,
    KOI-7913 AB, and Kepler-1627 compared to those of young open
    clusters and field stars. }
    The statistical uncertainties on the newly measured equivalent
    widths are shown, or else are smaller than the markers.
    The field stars are stars with Kepler planets from \citet{berger_identifying_2018}.
    The ``40-50 Myr'' reference stars (left) are from
		IC\,2602 \citep{randich_gaiaeso_2018} and Tuc-Hor
		\citep{kraus_stellar_2014}.
    The ``112 Myr'' stars (right) are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018},
    where we adopt the LDB age from \citet{dahm_2015}.
    \label{fig:lithium}
	}
\end{figure*}

@@

>>>>

\subsection{Further Work on Cep-Her}

Disentangling its kinematics
* Need an RV survey.

Benchmarking its age(s):
* Lithium analysis of FGK depletion (bright enough to be feasible).

* Asteroseismology of the delta Sct stars (TESS data are there, group is
rich enough).

Finding more interesting objects in it:
* Kepler data... presumably $\sim$200 stars in the cluster were
observed, in order to have detected 4 planets.

* TESS data

@@

{\bf LGB TODO: add Gaia source lists and abbreviated info.  Include rotation periods.}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown in the observed frame, and
    the stars are sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
			\includegraphics[width=0.49\textwidth]{f6b.pdf}
		}

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
		}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    Kepler objects of interest compared to young open clusters and
    field stars. }
    The statistical uncertainties on the newly measured equivalent
    widths are shown, or else are smaller than the markers.
    {\it Top}:
    The field stars are stars with Kepler planets from \citet{berger_identifying_2018}.
    The ``40-50 Myr'' reference stars (left) are from
		IC\,2602 \citep{randich_gaiaeso_2018} and Tuc-Hor
		\citep{kraus_stellar_2014}.
    The ``112 Myr'' stars (right) are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018},
    where the quoted LDB age os from \citet{dahm_2015}.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure*}

@@

\subsection{H$\alpha$}

As shown in Figure~\ref{fig:koiyouthindicators}, H$\alpha$ is in
emission for both components of KOI-7913, and in absorption for the
hotter stars.  Additionally, the emission appears double-peaked for
both of the KOI-7913 components.  We note that KOI-7913~A and
KOI-7913~B were spatially resolved from each other during data
acquisition.  Performing a cross-correlation between each of the stars
and the nearest matches in the Keck/HIRES template library, we also
found that the CCFs for both components of KOI-7913 showed no
indications of double-lined binarity \citep{kolbl_detection_2015}.

Balmer line emission, particularly for H$\alpha$, is expected for
stars of this age.  \citet{kraus_stellar_2014} for instance, in their
survey of Tuc-Hor ($\approx$40\,Myr), observed that essentially all
cluster members with spectral type $>$${\rm K4.5V}$ had H$\alpha$ in
emission.  The agrees with our observations that KOI-7913 shows
H$\alpha$ in emission for both components, while it is in absorption
for all of our other Kepler objects.  The double-peaked nature of the
emission, though not always present, is also not particularly rare for
active stars.  Proxima Centauri, for instance, has double-peaked
H$\alpha$ emission \citep{collins_calculations_2017}.  A simple
explanation is self-absorption: photons nearest the center of the line
see a greater optical depth from higher layers of the chromosphere,
while photons on the wings are on average too far from the
rest-wavelength to excite electrons and be re-absorbed in the upper
layers.  The exact details of when a star's atmosphere reaches the
conditions for such self-absorption require non-local thermal
equilibrium models of the chromosphere
\citep{short_chromospheric_1998,2005A&A...439.1137F}.
